Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-31 paper/paper.tex
fix plots

Open-source \nids{}, like Snort~\cite{snort} and
Suricata~\cite{suricata}, provide rulesets for many existing
attacks. Unfortunately, attackers actively look for new mechanisms to
\begin{wrapfigure}[8]{r}{0.21\textwidth}
    \vspace{-2ex}  
    \centering
    \scalebox{0.9}{  
      \begin{tikzpicture}
        \begin{axis}[
            width = 0.3\textwidth,
            height = 0.2\textwidth,            
            bar width=4pt,
            scaled ticks=false,
            ymajorticks=false,
            ybar stacked,
            enlargelimits=0.09,
            clip=true,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\footnotesize},
            tick pos=left,
            nodes near coords,
            every node near coord/.append style={font=\footnotesize},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-5ex}
    \caption{\label{fig:distribution-rules-per-month}2019 new rules.}
\end{wrapfigure}
exploit systems through the
network. Figure~\ref{fig:distribution-rules-per-month} shows the
number of rules added per month in the year of 2019 to the ``Emerging
Threats Open Ruleset''~\cite{emerging-threats-open}, a popular public
data set of \suri\ rules. A closer observation on the changelogs of
this ruleset~\cite{emerging-threats-changelogs} shows that new rules
are often created.  Rulesets need to be continuously revised as the
community finds and advertises vulnerabilities, which eventually can
be exploited by hackers.  Unfortunately, creating these rules is
time-consuming and error-prone~\cite{vollmer-etal-cics2011,alparslan-blog-suri}. The language for
describing rules is non-trivial (see
Section~\ref{sec:example-suricata-rules}) and testing correctness of a
rule requires data and careful inspection.

@@

  \scalebox{0.8}{  

@@

          enlargelimits=0.08,

@@

          xticklabel style={rotate=30},

@@

          enlargelimits=0.08,

@@

          enlargelimits=0.08,

@@

          enlargelimits=0.08,

>>>>

Open-source \nids{}, like Snort~\cite{snort} and
Suricata~\cite{suricata}, provide rulesets for many existing
attacks. Unfortunately, attackers actively look for new mechanisms to
\begin{wrapfigure}[8]{r}{0.21\textwidth}
    \vspace{-2ex}  
    \centering
    \scalebox{0.9}{  
      \begin{tikzpicture}
        \begin{axis}[
            width = 0.3\textwidth,
            height = 0.2\textwidth,            
            bar width=3pt,
            scaled ticks=false,
            ymajorticks=false,
            ybar stacked,
            ymax=250,
            enlargelimits=0.09,
            clip=true,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\footnotesize},
            tick pos=left,
            nodes near coords,
            every node near coord/.append style={font=\footnotesize},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-5ex}
    \caption{\label{fig:distribution-rules-per-month}2019 new rules.}
\end{wrapfigure}
exploit systems through the
network. Figure~\ref{fig:distribution-rules-per-month} shows the
number of rules added per month in the year of 2019 to the ``Emerging
Threats Open Ruleset''~\cite{emerging-threats-open}, a popular public
data set of \suri\ rules. A closer observation on the changelogs of
this ruleset~\cite{emerging-threats-changelogs} shows that new rules
are often created.  Rulesets need to be continuously revised as the
community finds and advertises vulnerabilities, which eventually can
be exploited by hackers.  Unfortunately, creating these rules is
time-consuming and error-prone~\cite{vollmer-etal-cics2011,alparslan-blog-suri}. The language for
describing rules is non-trivial (see
Section~\ref{sec:example-suricata-rules}) and testing correctness of a
rule requires data and careful inspection.

@@

  \scalebox{0.9}{  

@@

          ymax=28000,
          enlargelimits=0.12,

@@

@@

          ymax=10000,
          enlargelimits=0.1,

@@

          ymax=2200,
          enlargelimits=0.1,

@@

          ymax=11000,
          enlargelimits=0.12,
